Programming Distributed Control Planes

### 2016-01-21 paper/compilation.tex
Adding to compilation section.

  \begin{tikzpicture}[>=stealth',shorten >=1pt,auto,node distance=1.6cm]
    \state{0}{$0$}{              }{}
    \state{1}{$1$}{right of=0}{}
    \state{2}{$2$}{right of=1}{}
    \state{3}{$3$}{right of=2}{}
    \state{4}{$5$}{right of=3}{accepting}
    \transition{0}{1}{out}{}
    \transition{1}{2}{in}{}
    \transition{2}{2}{ACDE}{loop above}
    \transition{2}{3}{B}{}
    \transition{3}{3}{B}{loop above}
    \transition{3}{2}{ACDE}{bend left}
    \transition{3}{4}{W}{}
  \end{tikzpicture}

@@

\para{Construction}

@@

\todo{work out the exact details here}

>>>>

  \begin{tikzpicture}[>=stealth',shorten >=1pt,auto,node distance=1.6cm]
    \state{0}{$0$}{              }{}
    \state{1}{$1$}{right of=0}{}
    \state{2}{$2$}{right of=1}{}
    \state{3}{$3$}{right of=2}{}
    \state{4}{$4$}{right of=3}{accepting}
    \transition{0}{1}{out}{}
    \transition{1}{2}{in}{}
    \transition{2}{2}{ACDE}{loop above}
    \transition{2}{3}{B}{}
    \transition{3}{3}{B}{loop above}
    \transition{3}{2}{ACDE}{bend left}
    \transition{3}{4}{W}{}
  \end{tikzpicture}

@@

\para{Example}

@@

Consider the topology shown in Figure~\ref{fig:example-compilation}. Suppose we want to set up a primary route from W that enters the network from $A$, and utilizes the A -- C and C -- D links. We also would like a backup route that utilizes enters from node $B$, and utilizes the B -- C link, but is otherwise unconstrained. For the sake of simplicity, we will assume that the route can end in either $X$, $Y$, or $Z$. The RIR for the policy is:
%
$$(W \cdot A \cdot C \cdot D \cdot out) \gg (W \cdot B \cdot in^* \cdot out)$$
%
Figure~\ref{fig:example-compilation} shows the policy automata for each regular expression preference. Since we are interested in the flow of control messages, the automata match backwards. Figure~\ref{fig:example-compilation} shows the product graph obtained from intersecting the topology and policy automata. Every path in the product graph corresponds to a concrete path in the topology. In particular, every path through the product graph that ends at a node with an accepting preference is a valid topological path that satisfies the policy constraints and results in a particular preferenced path.
%
For example, the path $X D C A W$ is a valid path in the topology that BGP route advertisements might take, which would lead to obtaining the most prefered preference.
BGP control messages can start from peer X, which would match the $out$ transition from both automata, leading to state $1$ in the first automaton, and state $1$ in the second automaton. This is reflected in the product graph by the node with state $(1,1) X$. From here, if X were to advertise this route to D, it would result in the path $D X$, which would lead to state $2$ in the first automaton, and state $2$ in the second automaton, and so on. Since node $(5,-) W$ is in an accepting state for the first automata, it indicates this path has preference 1.

\todo{explain drop states}
\todo{preferences are reversed in picture}

\para{Minimization}

TODO
